Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-02-26 abstract.tex
working on the abstract...

>>>>

% 
This article presents a seismic hazard assessment for northern Iran, using a smoothed seismicity approach in combination with an updated seismic catalog and a recently introduced ground motion prediction equation. In the assessment, we evaluate the hazard considering the contribution of the three major seismic zones affecting the northern part of the country, namely Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh. For completeness, we also consider the partial contribution of the two remaining seismic zones of Zagros and the central and eastern

% Ricardo is working on this...

,  and

recently introduced

 We conduct an assessment of seismic hazard for northern Iran using
